Two Problems for Sophistication

### 2015-01-21 Facticity/Facticity/paper.tex
...

We sometimes need to map binary strings to a prefix-free set. We denote by $\br{x}$ the prefix-encoded representation for $x$. We require that the mapping satisfies $|\br{x}| = |x|+O(\log(|x|)$ (see eg. \cite[Section~1.4]{li1993introduction}). To simplify notation, we will sometimes conflate natural numbers and binary strings, implicitly using the ordering $(0, \epsilon)$, $(1, 0)$, $(2, 1)$, $(3, 00)$, $(4, 01)$, \ldots 
Now define the Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows $C^{\M,\psi}(x)=\min\{\bar\imath y:\psi_i(y)=x,i\in\M\}$. The model classes $\C$ and $\K$ give us the plain and prefix-free Kolmogorov complexity repectively.

\section{Inefficient indices}
\label{section:indices}
In some works, the definition of sophistication is obtained by opening up the definition of Kolmogorov complexity, and measuring the length of the index part of that two-part code. We call such a sophistication \emph{index sophistication}. Examples are Koppel and Atlan's works \cite{koppelSoph1988,koppel1991almost},  and several of its variants \cite{antunes2009sophistication,antunes2013sophistication}.

>>>>

We sometimes need to map binary strings to a prefix-free set. We denote by $\br{x}$ the prefix-encoded representation for $x$. We require that the mapping satisfies $|\br{x}| = |x|+O(\log(|x|)$ (see eg. \cite[Section~1.4]{li1993introduction}). To simplify notation, we will sometimes conflate natural numbers and binary strings, implicitly using the ordering $(0, \epsilon)$, $(1, 0)$, $(2, 1)$, $(3, 00)$, $(4, 01)$, \ldots  
We define the $\M$-Kolmogorov complexity of a binary string $x$, with respect to a model class $\M$ and a numbering $\psi$, as follows $C^{\M,\psi}(x)=\min\{\bar\imath y:\psi_i(y)=x,i\in\M\}$. The model classes $\C$ and $\K$ give us the plain and prefix-free Kolmogorov complexity respectively.

\section{Inefficient indices}
\label{section:indices}
In some works, the definition of sophistication is obtained by opening up the definition of Kolmogorov complexity, and measuring the length of the index in that two-part code. We call such a sophistication \emph{index sophistication}. Examples are Koppel and Atlan's works \cite{koppelSoph1988,koppel1991almost},  and several of its variants \cite{antunes2009sophistication,antunes2013sophistication}.
